Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Revising intro
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1627 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\textbf{Joshua} is an open-source toolkit for parsing-based machine translation (written in Java). The initial release of Joshua  \cite{joshua-wmt09} was a re-implementation of the Hiero system \cite{hiero-2007} and all its associated algorithms, including: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  The Joshua release also included re-implementations of suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007,PBML-2010-Joshua-grammar-extraction}  and minimum error rate training \cite{och-mert,Zaidan2009}.  Additionally, it included parallel and distributed computing techniques for salability \cite{Joshua-old}.

This paper describes the additions to the toolkit over the past year, which together form the 2.0 release. The software has been heavily used by the authors and several other groups in their daily research, and has been substantially refined since the first release.  The most important new functions in the toolkit are: 
\begin{itemize}
\item
support for the syntax-augmented machine translation (SAMT) grammar \cite{samt2006},
\item
support for external modules to posit translations for spans in the input sentence that constrain decoding,    \cite{PBML-2010-Joshua-transliteration},  
\item
lattice parsing for dealing with input uncertainty \cite{dyer-muresan-resnik:2008:ACLMain},
\item
semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
variational decoding for approximating the intractable MAP decoding \cite{variational-decoding-acl09},
\item
hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
visualization of the derivation trees and hypergraphs \cite{PBML-2010-Joshua-visualization}, 
\item
and a unified framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.

>>>>

\textbf{Joshua} is an open-source toolkit for parsing-based machine translation that is written in Java. The initial release of Joshua  \cite{joshua-wmt09} was a re-implementation of the Hiero system \cite{hiero-2007} and all its associated algorithms, including: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  The Joshua 1.0 release also included re-implementations of suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007,PBML-2010-Joshua-grammar-extraction}  and minimum error rate training \cite{och-mert,Zaidan2009}.  Additionally, it included parallel and distributed computing techniques for salability \cite{Joshua-old}.

This paper describes the additions to the toolkit over the past year, which together form the 2.0 release. The software has been heavily used by the authors and several other groups in their daily research, and has been substantially refined since the first release.  The most important new functions in the toolkit are: 
\begin{itemize}
\item
Support for any style of synchronous context free grammar (SCFG)
% instead of just Hiero grammars.  This 
including syntax augment machine translation (SAMT) grammars \cite{samt2006},
\item
Support for external modules to posit translations for spans in the input sentence that constrain decoding,    \cite{PBML-2010-Joshua-transliteration},  
\item
Lattice parsing for dealing with input uncertainty, including ambiguous output from speech recognizers or Chinese word segmenters  \cite{dyer-muresan-resnik:2008:ACLMain},
\item
Semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
Improvements to decoding through variational methods and approximations to intractable MAP decoding \cite{variational-decoding-acl09},
\item
Hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
Visualization of the derivation trees and hypergraphs \cite{PBML-2010-Joshua-visualization}, 
\item
A unified framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.
